R for Clinical Study Reports and Submission

### 2023-07-16 tlf-baseline.qmd
add package use case

```{r}
library(haven)
library(dplyr)
library(tidyr)
library(stringr)
library(tools)
library(table1)
library(r2rtf)
```

>>>>

```{r}
library(haven)   # Read SAS data
library(dplyr)   # Manipulate data
library(tidyr)   # Manipulate data
library(stringr) # Manipulate string
library(tools)   # Manipulate string
library(table1)  # Baseline characteristics table
library(r2rtf)   # Reporting in RTF format
```
